### 2021-09-11 preprint.tex
Deploy to GitHub Pages

%!TEX TS-program = xelatex
\documentclass[11pt]{article}

@@

\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[3] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc} % for \widthof, \maxof
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\maxof{\widthof{#1}}{\csllabelwidth}}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth}{#1}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}\geometry{verbose,letterpaper,tmargin=2.5cm,bmargin=2.5cm,lmargin=2.5cm,rmargin=4.5cm}

\usepackage{lineno}
\usepackage[nolists,noheads]{endfloat}

@@

\doublespacing

\fancypagestyle{normal}
{
  \fancyhf{}
  \fancyfoot[R]{\footnotesize\sffamily\thepage\ of \pageref*{LastPage}}
}
\begin{document}
\thispagestyle{empty}
{\Large\bfseries\sffamily Food web reconstruction through phylogenetic
transfer of low-rank network representation}
\vskip 5em

%
\href{https://orcid.org/0000-0001-6067-1349}{Tanya\,Strydom}%
%
\,\textsuperscript{1,2,‡}\quad %
\href{https://orcid.org/0000-0003-0193-5441}{Salomé\,Bouskila}%
%
\,\textsuperscript{1,‡}\quad %
\href{https://orcid.org/0000-0001-9051-0597}{Francis\,Banville}%
%
\,\textsuperscript{1,3,2}\quad %
\href{https://orcid.org/0000-0003-4036-977X}{Ceres\,Barros}%
%
\,\textsuperscript{4}\quad %
\href{https://orcid.org/0000-0002-2151-6693}{Dominique\,Caron}%
%
\,\textsuperscript{5,2}\quad %
\href{https://orcid.org/0000-0003-0452-6993}{Maxwell J\,Farrell}%
%
\,\textsuperscript{6}\quad %
\href{https://orcid.org/0000-0002-9935-1366}{Marie-Josée\,Fortin}%
%
\,\textsuperscript{6}\quad %
\href{https://orcid.org/0000-0003-3220-6161}{Victoria\,Hemming}%
%
\,\textsuperscript{4}\quad %
\href{https://orcid.org/0000-0002-4104-9463}{Benjamin\,Mercier}%
%
\,\textsuperscript{3,2}\quad %
\href{https://orcid.org/0000-0002-6004-4027}{Laura J.\,Pollock}%
%
\,\textsuperscript{5}\quad %
\href{https://orcid.org/0000-0001-5785-8321}{Rogini\,Runghen}%
%
\,\textsuperscript{7}\quad %
\href{https://orcid.org/0000-0002-3454-0633}{Giulio V.\,Dalla Riva}%
%
\,\textsuperscript{8}\quad %
\href{https://orcid.org/0000-0002-0735-5184}{Timothée\,Poisot}%
%
\,\textsuperscript{1,2}

\textsuperscript{1}\,Département de Sciences Biologiques, Université de
Montréal, Montréal, Canada\quad \textsuperscript{2}\,Québec Centre for
Biodiversity Sciences, Montréal,
Canada\quad \textsuperscript{3}\,Université de Sherbrooke, Sherbrooke,
Canada\quad \textsuperscript{4}\,Department of Forest Resources
Management, University of British Columbia, Vancouver,
Canada\quad \textsuperscript{5}\,Department of Biology, McGill
University, Montréal, Canada\quad \textsuperscript{6}\,Department of
Ecology \& Evolutionary Biology, University of Toronto, Toronto,
Canada\quad \textsuperscript{7}\,Centre for Integrative Ecology, School
of Biological Sciences, University of Canterbury, Canterbury, New
Zealand\quad \textsuperscript{8}\,School of Mathematics and Statistics,
University of Canterbury, Canterbury, New Zealand

\textsuperscript{‡}\,These authors contributed equally to the work\\

\textbf{Correspondance to:}\\
Timothée Poisot --- \texttt{timothee.poisot@umontreal.ca}\\

\vfill
This work is released by its authors under a CC-BY 4.0 license\hfill\ccby\\
Last revision: \emph{\today}

\clearpage
\thispagestyle{empty}

\vfill
\textbf{\sffamily Abstract: }Despite their importance in many ecological
processes, collecting data and information on ecological interactions,
and therefore species interaction networks, is an exceedingly
challenging task. For this reason, large parts of the world have a
deficit of data of which species interact, and what we can expect the
network structure of these interactions to be. As data collection alone
is unlikely to be sufficient at filling these global gaps, community
ecologists must adopt predictive methods. In this contribution we
develop such a method, relying on graph embedding (the extraction of
explanatory latent variables from known graph structures) and transfer
learning (the application of previous solution to novel problems with
limited predictors overlap) in order to assemble a predicted list of
trophic interactions between mammals of Canada. This interaction list is
derived from extensive knowledge of the mammalian food web of Europe,
despite the fact that there are fewer than 5\% of common species between
the two locations. We provide guidance on how this method can be adapted
by substituting some approaches or predictors in order to make it more
generally applicable to a broad family of ecological problems.
\vfill

\clearpage
\linenumbers
\pagestyle{normal}

>>>>

%!TEX TS-program = xelatex
\documentclass[10pt,oneside]{article}

@@

\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[3] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc} % for \widthof, \maxof
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\maxof{\widthof{#1}}{\csllabelwidth}}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth}{#1}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}\usepackage[table,dvipsnames]{xcolor}

\geometry{includemp,
            letterpaper,
            top=1.2in,
            bottom=2.510cm,
            inner=0.5in,
            outer=0.4in,
            marginparwidth=1.95in,
            marginparsep=0.4in}

\usepackage[singlelinecheck=off]{caption}
\captionsetup{
  font={small},
  labelfont={bf},
  format=plain,
  labelsep=quad
}
\usepackage{floatrow}
\floatsetup[figure]{margins=hangright,
              facing=no,
              capposition=beside,
              capbesideposition={center,outside},
              floatwidth=\textwidth}
\floatsetup[table]{margins=hangoutside,
             facing=yes,
             capposition=beside,
             capbesideposition={center,outside},
             floatwidth=\textwidth}

@@

\setcounter{secnumdepth}{5}

\usepackage{titlesec}

\titleformat{\section}[block]
{\normalfont\large\sffamily}
{\thesection}{.5em}{\titlerule\\[.8ex]\bfseries}

\titleformat{\subsection}[runin]
{\normalfont\fontseries{b}\selectfont\filright\sffamily}
{\thesubsection.}{.5em}{}

\titleformat{\subsubsection}[runin]
{\normalfont\itshape\rmfamily\bfseries}{\thesubsubsection}{1em}{}

\fancypagestyle{firstpage}
{
   \fancyhf{}
   \renewcommand{\headrulewidth}{0pt}
   \fancyfoot[R]{\footnotesize\ccby}
   \fancyfoot[L]{\footnotesize\sffamily\today}
}

\fancypagestyle{normal}
{
  \fancyhf{}
  \fancyfoot[R]{\footnotesize\sffamily\thepage\ of \pageref*{LastPage}}
}

\usepackage{tikz}
\begin{document}
\tikz [remember picture, overlay] %
\node [shift={(-0.6in,1.1cm)},scale=0.2,opacity=0.4] at (current page.south east)[anchor=south east]{\includegraphics{logo}};%
\pagestyle{normal}
\thispagestyle{firstpage}

\newcommand{\colorRule}[3][black]{\textcolor[HTML]{#1}{\rule{#2}{#3}}}

\noindent {\LARGE \textbf{\textsf{Food web reconstruction through
phylogenetic transfer of low-rank network representation}}}

\medskip
\begin{flushleft}
{\small
%
\href{https://orcid.org/0000-0001-6067-1349}{Tanya\,Strydom}%
%
\,\textsuperscript{1,2,‡}, %
\href{https://orcid.org/0000-0003-0193-5441}{Salomé\,Bouskila}%
%
\,\textsuperscript{1,‡}, %
\href{https://orcid.org/0000-0001-9051-0597}{Francis\,Banville}%
%
\,\textsuperscript{1,3,2}, %
\href{https://orcid.org/0000-0003-4036-977X}{Ceres\,Barros}%
%
\,\textsuperscript{4}, %
\href{https://orcid.org/0000-0002-2151-6693}{Dominique\,Caron}%
%
\,\textsuperscript{5,2}, %
\href{https://orcid.org/0000-0003-0452-6993}{Maxwell J\,Farrell}%
%
\,\textsuperscript{6}, %
\href{https://orcid.org/0000-0002-9935-1366}{Marie-Josée\,Fortin}%
%
\,\textsuperscript{6}, %
\href{https://orcid.org/0000-0003-3220-6161}{Victoria\,Hemming}%
%
\,\textsuperscript{4}, %
\href{https://orcid.org/0000-0002-4104-9463}{Benjamin\,Mercier}%
%
\,\textsuperscript{3,2}, %
\href{https://orcid.org/0000-0002-6004-4027}{Laura J.\,Pollock}%
%
\,\textsuperscript{5}, %
\href{https://orcid.org/0000-0001-5785-8321}{Rogini\,Runghen}%
%
\,\textsuperscript{7}, %
\href{https://orcid.org/0000-0002-3454-0633}{Giulio V.\,Dalla Riva}%
%
\,\textsuperscript{8}, %
\href{https://orcid.org/0000-0002-0735-5184}{Timothée\,Poisot}%
%
\,\textsuperscript{1,2}
\vskip 1em
\textsuperscript{1}\,Département de Sciences Biologiques, Université de
Montréal, Montréal, Canada; \textsuperscript{2}\,Québec Centre for
Biodiversity Sciences, Montréal, Canada; \textsuperscript{3}\,Université
de Sherbrooke, Sherbrooke, Canada; \textsuperscript{4}\,Department of
Forest Resources Management, University of British Columbia, Vancouver,
Canada; \textsuperscript{5}\,Department of Biology, McGill University,
Montréal, Canada; \textsuperscript{6}\,Department of Ecology \&
Evolutionary Biology, University of Toronto, Toronto,
Canada; \textsuperscript{7}\,Centre for Integrative Ecology, School of
Biological Sciences, University of Canterbury, Canterbury, New
Zealand; \textsuperscript{8}\,School of Mathematics and Statistics,
University of Canterbury, Canterbury, New Zealand\\
\textsuperscript{‡}\,These authors contributed equally to the work\\
\vskip 1em
\textbf{Correspondance to:}\\
Timothée Poisot --- \texttt{timothee.poisot@umontreal.ca}\\
}
\end{flushleft}

\vskip 2em
\makebox[0pt][l]{\colorRule[CCCCCC]{2.0\textwidth}{0.5pt}}
\vskip 2em
\noindent

\marginpar{\vskip 1em\flushright
{\small{\bfseries Keywords}:\par
ecological networks\\network embedding\\transfer learning\\ancestral
character estimation\\biogeography\\}
}

\textbf{Abstract}:\,Despite their importance in many ecological
processes, collecting data and information on ecological interactions,
and therefore species interaction networks, is an exceedingly
challenging task. For this reason, large parts of the world have a
deficit of data of which species interact, and what we can expect the
network structure of these interactions to be. As data collection alone
is unlikely to be sufficient at filling these global gaps, community
ecologists must adopt predictive methods. In this contribution we
develop such a method, relying on graph embedding (the extraction of
explanatory latent variables from known graph structures) and transfer
learning (the application of previous solution to novel problems with
limited predictors overlap) in order to assemble a predicted list of
trophic interactions between mammals of Canada. This interaction list is
derived from extensive knowledge of the mammalian food web of Europe,
despite the fact that there are fewer than 5\% of common species between
the two locations. We provide guidance on how this method can be adapted
by substituting some approaches or predictors in order to make it more
generally applicable to a broad family of ecological problems.

\vskip 2em
\makebox[0pt][l]{\colorRule[CCCCCC]{2.0\textwidth}{0.5pt}}
\vskip 2em
